\renewcommand{\parttitle}{Numerical Code}
\setlength{\parskip}{0pt}

\section*{Overview}
This document provides the execution instructions for the numerical code submitted for Assignment 1.
The numerical work is split into two MATLAB files:
\begin{itemize}\itemsep=0pt\parsep=0pt
\item \texttt{Camile\_BRIARD\_aeroelastic\_assign1\_notebook.mlx}: results for Questions 1 to 5;
\item \texttt{Camile\_BRIARD\_q6\_assign1.m}: result for Question 6.
\end{itemize}
\vspace{2em}
\noindent
\begin{minipage}[t]{0.30\textwidth}
\section*{Software}
\begin{itemize}\itemsep=0pt\parsep=0pt
\item Software used: MATLAB
\item MATLAB release : \textbf{R2025b}
\item Full version string : \textbf{25.2.0.2998904}
\end{itemize}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.63\textwidth}
\section*{Required Libraries and Dependencies}
No external library, package, or user-defined dependency is required outside MATLAB itself.
The submitted files use only standard MATLAB functionality, including Live Script support for the \texttt{.mlx} notebook.
\end{minipage}
\section*{Execution Instructions}
\subsection*{Questions 1 to 5}
File to run: \texttt{Camile\_BRIARD\_aeroelastic\_assign1\_notebook.mlx} Recommended execution procedure:
\begin{enumerate}\itemsep=0pt\parsep=0pt
\item Open MATLAB.
\item Set the repository root as the current folder.
\item Open the file \texttt{Camile\_BRIARD\_aeroelastic\_assign1\_notebook.mlx}.
\item Run the full Live Script with \texttt{Run All}.
\end{enumerate}
Expected runtime:
\begin{itemize}\itemsep=0pt\parsep=0pt
\item approximately 1 minute on a machine equivalent to an Intel i9 with 16 GB RAM;
\item allow about 1 to 3 minutes for full execution.
\end{itemize}
During execution, the notebook computes the numerical results and generates the figures used in the report.
The notebook file is intentionally submitted as a Live Script because it contains both commented explanations and numerical sections for Questions 1 to 5.
Do not take into account the error about \texttt{ME.message}, it does not affect the execution and the results.
\subsection*{Question 6}
File to run: \texttt{Camile\_BRIARD\_q6\_assign1.m} The notebook and the script are independent and can be executed separately. Recommended execution procedure:
\begin{enumerate}\itemsep=0pt\parsep=0pt
\item Open MATLAB.
\item Set the repository root as the current folder.
\item Open the file \texttt{Camile\_BRIARD\_q6\_assign1.m}.
\item Open the \texttt{Command Window} to view printed outputs.
\item Run the script.
\end{enumerate}